Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-27 prob.tex
prob.tex \section{Proof} Updating...

Here we want to follow \cite{RichmanBridges1999} to prove under suitable
conditions when intervals are more precise, its quantum interval-valued
probability measures are closer to the Born rule. We will focus on
three dimensional Hilbert space, since

>>>>

\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
is denoted by $S^{d-1}$.\qed\end{definition}

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ is
called an \emph{approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if 
\[
W_{l}\le\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{d-1}}f\left(\ket{\psi_{i}}\right)\le W_{r}
\]
 for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$.\qed\end{definition}

\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}

\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a frame function of weight~$\left(W_{l},W_{r}\right)$, and $\ket{\psi}\in S^{2}$,
then the \emph{symmetrization} of $f$ with respect to $\ket{\psi}$
is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
\[
g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
\]
where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}

The following theorem is an analog to Corollary 22 in \cite{RichmanBridges1999}.

\begin{thm}Let $f$ be an bounded continuous frame function of weight~$\left(W_{l},W_{r}\right)$,
$m=\inf f$ or $m=\sup f$, and $W=\left(W_{l}+W_{r}\right)/2$. Let
$Q$ be the quadratic form given by
\[
Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
\]
For each $\delta>0$, there is $\eta>0$ such that if
\begin{itemize}
\item $\ket{\psi}\in S^{2}$such that $\left|f\left(\ket{\psi}\right)-m\right|<\eta$,
and 
\item $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$.
\end{itemize}
then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\omega_{f}^{-1}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$.\qed\end{thm}

We can see that for a
